Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-12 WSSSPE2_report/WSSSPE2_review.tex
added citation and fiex flow in incentives section

The discussion of incentivizing those in science acknowledged that the publications system was far from perfect for incentivizing good software work.
Nonetheless discussion focused on bringing software people into publications. There were two main suggestions.
The first is to focus on end users of software and encourage them to cite software the ``right" way. \katznote{what is the second?}
James Howison suggested that his research showed that few projects were making a formal request for citation (but that authors weren't necessarily following those suggestions anyway) \katznote{add cite?}; he suggested making access to the software conditional on a license that requires citation.
Others found this ``too confrontational" and preferred to concentrate on making it easier to do the right thing.
The group was more enthusiastic about ``forcing" PIs to include their ``software people" on publications, although there were few ideas on how exactly to do this.
Another technique mentioned was that when scientific software projects are hosted in organizations like Apache, the scientific contributors can benefit from building their reputations, perhaps yielding job offers that they can use to negotiate better job and career packages.

>>>>

The discussion of incentivizing those in science acknowledged that the publications system was far from perfect for incentivizing good software work.
Nonetheless discussion focused on bringing software people into publications. There were two main suggestions.
The first is to focus on end users of software and encourage them to cite software the ``right" way.
James Howison suggested that his research showed that few projects were making a formal request for citation (but that authors weren't necessarily following those suggestions anyway) \cite{howison2015jasist} he suggested making access to the software conditional on a license that requires citation.
Others found this ``too confrontational" and preferred to concentrate on making it easier to do the right thing.
The second was focusing on those leading software projects, and the group was more enthusiastic about ``forcing" PIs to include their ``software people" on publications, although there were few ideas on how exactly to do this.
Another technique mentioned was that when scientific software projects are hosted in organizations like Apache, the scientific contributors can benefit from building their reputations, perhaps yielding job offers that they can use to negotiate better job and career packages.
